---
title: "R Notebook"
author: "Alyssa Knapp"
date: "12/10/20" 
output: html_notebook
---

# Final Project: UFO Sightings & U.S. Air Quality 

## Research Question

Where are UFO sightings in the United States associated with pollutant levels of carbon monoxide (CO) and nitrogen dioxide (NO2) from 2000 to 2008?


## Purpose

This topic is important to investigate because there is currently very little knowledge of how climate information relates to UFO sightings. Air quality, in particular, is interesting to explore because air pollutants can impair visibility, which may affect the ability of UFOs to be seen in the sky. This "relationship" is expected to become more polarized over time, as air quality worsens. 


## Data Access

```{r, message = FALSE, warning = FALSE}
library(mosaic)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(knitr)
library(lubridate)
library(readxl)
library(DataComputing)
```

```{r}
rm(list=ls())
```

```{r}
#Data Set 1
UFO <- read_excel("UFOs_coord.xlsx")
```

```{r}
#Data Set 2
AirQ <- read.csv("UFOPOLLUTANTS.csv", header = TRUE)
```


## Inspecting Data Sets

```{r}
#Data Set 1
kable(head(UFO))
glimpse(UFO)
str(UFO)
```

```{r}
#Data Set 2
kable(head(AirQ))
glimpse(AirQ)
str(AirQ)
```


## Variables To Be Used (originally included in data sets)

Data Set 1
* country: limited only to USA
* state: records data from certain states 

Data Set 2 
* state: records data from certain states
* month: all 12 months
* year: contains data from 2000 to 2008

* NO2/CO Mean: mean concentration within a given day
* NO2/CO AQI: Air quality index within a given day
* NO2/CO 1st Max Value: maximum value obtained within a given day
* NO2/CO 1st Max Hour: the hour when the maximum concentration was obtained
* ET: equal to 1 if a UFO was sighted, 0 otherwise (binary)


##



